---
title: "Progress Memo 2 - Predicting Social Media Shares"
subtitle: |
  | What Indicators Can Predict Social Media Shares of Mashable News Articles?
author: "Stacy Caeiro"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---

::: {.callout-tip icon=false}

## Github Repo Link

[Final-Project-GitHub-Link](https://github.com/stat301-2-2024-winter/final-project-2-stacycaeiro.git)

:::

```{r}
#| echo: false
library(tidyverse)
library(tidymodels)
library(here)

load(here("results/null_results.rda"))
load(here("results/lm_results.rda"))
```

## Project Overview 
My final project is to predict the number of social media shares a Mashable news article will receive. Thus, I will be computing regression models to model the outcome of the numeric variable `shares`. Additionally, I will be using the [Online News Popularity](https://archive.ics.uci.edu/dataset/332/online+news+popularity) from the [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/).

## Assessment Metric 
I will be using root standard mean error (RMSE) as my assessment metric. 

## Analysis Plan 
To begin, I will split my data using stratified sampling such that 80% of the data is used for training and 20% is used for testing. Furthermore, I will use v-fold cross-validation resampling with 5 folds and 3 repeats. 

For my project, I will use 6 models: null, linear, lasso, random forest, k-nearest neighbors, and boosted tree. 

Additionally, I will use 3 recipes: a basic kitchen sink recipe for the null and linear models, a feature engineering recipe for the lasso and k-nearest neighbors models, and a feature engineering recipe for the tree models (random forest and boosted tree). 


## Model Results 
```{r}
#| echo: false
bind_rows(null_results, lm_results) |>
  knitr::kable()
```
As seen here, the mean RMSE for the null model is `0.928` and the mean RMSE for the linear model is `1.11`. By these metrics, the null model performed better than the linear model. 

## Summary of Progress & Next Steps
So far, I have cleaned and split my data, created one basic kitchen sink recipe, and fit a null model and a linear model. My next steps are to conduct an EDA to determine what feature engineering steps to add to my recipes & what hyperparameters to tune. Then, I will need to create the final 2 recipes, fit the final 4 models, and collect metrics.