---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 2 with R (STAT 301-2)
author: "Stacy Caeiro"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
reference-location: margin
citation-location: margin
---


::: {.callout-tip icon=false}

## Github Repo Link

[Final-Project-GitHub-Link](https://github.com/stat301-2-2024-winter/final-project-2-stacycaeiro.git)

:::

```{r}
#| echo: false

library(tidyverse)
library(here)
```

## Prediction Problem 

My prediction problem is to predict the amount of social media shares a news 
article will receive. The target variable is `shares`, which is a numeric variable,
so the model will be a regression. I am choosing this problem because increasing 
social media shares is a common business goal. The results of this model can 
act as a guide to other publishing sites on how to increase their social media 
visibility. Additionally, this is a real-world problem I may be faced with when I enter the workforce. 

## Data source

For my final project I will be using the [Online News Popularity](https://archive.ics.uci.edu/dataset/332/online+news+popularity) 
from the [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/). This
dataset contains features of Mashable news articles, such as length of title and 
date of the week published, that were published over a 2 year period. 

## Data quality & complexity check

There are 39,644 observations and 61 variables. Of these variables, two are non-predictive (`url` and `timedelta`), one is the target variable (`shares`), and the remaining 58 are predictive variables. As of now, all the variables in the dataset are numeric. However, some variables will need to be pivoted and converted into factor variables, such as the `weekday_is_`, `data_channel_is_`, and `is_weekend` variables.
Furthermore, this dataset contains no missing values. 


```{r}
#| echo: false 

news_articles <- read_csv(here("data/OnlineNewsPopularity.csv"))

news_articles |> 
  head()
```


## Potential data issues

Although there are 58 predictor variables, due to computer restraints, I may need 
to downsize the dataset to only include 15-40 variables. 

## Target Variable Analysis 

```{r}
#| echo: false

ggplot(news_articles, aes(x = shares)) + 
  geom_histogram() + 
  labs(title = "Frequency of Shares",
       x = "Shares",
       y = "Count")
```

While not immediately apparent in this histogram, there are
a few outliers in `shares`, with the max value being 843,300 shares. 

```{r}
#| echo: false

ggplot(news_articles, aes(x = shares)) +
  geom_histogram() + 
  xlim(0, 75000) + 
  ylim(0, 17500) + 
  labs(title = "Frequency of Shares",
       x = "Shares",
       y = "Count")
```
Upon zooming into the histogram, `shares` is right-skewed, as
fewer amounts of articles receive high amounts of shares. In fact, most articles only recieve around 10,000 or less shares. 

